HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
correction of examples

\paragraph{Machine Translation Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language \cite{lopez2008statistical}.
Human evaluation is generally determined
either according to the relative ranking of the outputs of multiple systems
e.g., in the WMT shared tasks \cite{bojar2015findings}, or by assigning
individual adequacy/fluency scores to each translation, a procedure recently improved
by \newcite{graham2015improving}.
However, while providing the gold standard for MT evaluation, human evaluation is not a scalable solution,
and is unfeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Most commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a reference translation,
whose validity has been manually confirmed. This decomposition further allows system developers
to localize the errors or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
the BLEU \cite{Papineni:2002}, NIST \cite{Doddington:2002} and METEOR measures \cite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
by applying string edit distance \cite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments,
their decomposition over words and n-grams is better suited for localizing errors
in the output of shallow MT methods, and is less instructive in identifying the semantic
nature of the errors.

@@

UCCA's current inventory of distinctions focuses on argument structures
(adjectival, nominal, verbal and others) and relations between them.
The most basic notion is the Scene, which describes a movement, an
action or a state which is persistent in time. Each Scene contains one main relation, as well
as one or more participants. For example, the sentence ``After graduation, Tom moved to NYC''
contains two Scenes, whose main relations are ``graduation'' and ``Tom''.
The participant ``John'' is a part of both Scenes, while ``NYC'' only of the
latter (\figref{fig:ucca_example}). Further categories account for
relations between Scenes and the internal structures of complex participants and relations.

@@

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
%   \begin{tikzpicture}
%     [level 1/.style={sibling distance=7.5em},
%       level 2/.style={sibling distance=5em},
%       level 3/.style={sibling distance=5em},
%       level 4/.style={sibling distance=3em}]
%     %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
%     %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
%   \node (ROOT) [label={B}] [fill=blue, circle] {}
%   child {node (H3) [label={A}] [fill=yellow,circle] {}
%     child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
%     child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
%       child {node [label={}] {became} edge from parent node[left]  {}}
%       child {node [label={}] {a} edge from parent node[left]  {}}
%       child {node [label={}] {passion} edge from parent node[left]  {}}
%     }
%     child {node (H2) [label={A}] [fill=yellow,circle] {}
%       child {node {} edge from parent[draw=none] {}}
%       child {node {} edge from parent[draw=none] {}}
%       child {node {} edge from parent[draw=none] {}}
%       child {node {} edge from parent[draw=none] {}}
%       child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
%       child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
%       child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
%       child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
%     }
%   }
%   child {node {} edge from parent[draw=none] {}}
%   child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
%     child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
%     child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
%     child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
%     child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
%   }
%   child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
%   child {node (H5) [label={A}] [fill=yellow,circle] {}  
%     child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
%     child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
%   };
%   \draw[dashed] (H5) -> (she) ;
% 
%   \com{
%   child {node (H1) [label={\#8}] [fill=black,circle] {}
%     child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
%       %child {node {to Paris} edge from parent node[right] {$A$}}
%       edge from parent node[left] {$H$}
%     }
%     child {node (H2) [label={\#9}] [fill=black,circle] {}
%       child {node  {} edge from parent[draw=none]}
%       child {node  {} edge from parent[draw=none]}
%       child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
%       child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
%       child {node [label={\#10}] [fill=black,circle] {}
%         child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
%         child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
%         edge from parent node[right] {$A$}}
%       %child {node {to Paris} edge from parent node[right] {$A$}}
%       edge from parent node[left] {$H$}
%     };
%     \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
%     }
%   \end{tikzpicture}
  \\
  \end{adjustbox}
  \adjustbox{width=\textwidth,center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}

>>>>

\paragraph{Machine Translation Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language \cite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT shared tasks \cite{bojar2015findings}, or by assigning
individual adequacy/fluency scores to each translation, a procedure recently improved
by \newcite{graham2015improving}.
However, while providing the gold standard for MT evaluation, human evaluation is not a scalable solution,
and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Most commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition further allows system developers
to localize the errors, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \cite{Papineni:2002}, NIST \cite{Doddington:2002} and METEOR  \cite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
by applying string edit distance \cite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments,
their decomposition over words and n-grams is better suited for localizing errors
in the output of shallow MT methods, and is less instructive in identifying the semantic
nature of the errors.

@@

UCCA's current inventory of distinctions focuses on argument structures
(adjectival, nominal, verbal and others) and relations between them.
The most basic notion is the Scene, which describes a movement, an
action or a state which is persistent in time. Each Scene contains one main relation, as well
as one or more participants. For example, the sentence ``After graduation, Tom moved to NYC''
contains two Scenes, whose main relations are ``graduation'' and ``moved''.
The participant ``Tom'' is a part of both Scenes, while ``NYC'' only of the
latter (\figref{fig:ucca_example}). Further categories account for
relations between Scenes and the internal structures of complex participants and relations.

@@

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
   \begin{tikzpicture}
     [level 1/.style={sibling distance=7.5em},
       level 2/.style={sibling distance=5em},
       level 3/.style={sibling distance=5em},
       level 4/.style={sibling distance=3em}]
     %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
     %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
   \node (ROOT) [label={B}] [fill=blue, circle] {}
   child {node (H3) [label={A}] [fill=yellow,circle] {}
     child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
     child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
       child {node [label={}] {became} edge from parent node[left]  {}}
       child {node [label={}] {a} edge from parent node[left]  {}}
       child {node [label={}] {passion} edge from parent node[left]  {}}
     }
     child {node (H2) [label={A}] [fill=yellow,circle] {}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
       child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
       child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
       child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
     }
   }
   child {node {} edge from parent[draw=none] {}}
   child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
     child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
   }
   child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
   child {node (H5) [label={A}] [fill=yellow,circle] {}  
     child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
     child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
   };
   \draw[dashed] (H5) -> (she) ;

   \com{
   child {node (H1) [label={\#8}] [fill=black,circle] {}
     child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
       %child {node {to Paris} edge from parent node[right] {$A$}}
       edge from parent node[left] {$H$}
     }
     child {node (H2) [label={\#9}] [fill=black,circle] {}
       child {node  {} edge from parent[draw=none]}
       child {node  {} edge from parent[draw=none]}
       child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
       child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
       child {node [label={\#10}] [fill=black,circle] {}
         child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
         child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
         edge from parent node[right] {$A$}}
       %child {node {to Paris} edge from parent node[right] {$A$}}
       edge from parent node[left] {$H$}
     };
     \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
     }
   \end{tikzpicture}
  \\
  \end{adjustbox}
  \adjustbox{width=\textwidth,center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}
